Naturalness and Long-Lived Beyond the Standard Model Particles

### 2017-08-04 tex/draft.tex
Address comments

    Experimentally, the $\Wpm$, $\Z$, quarks, and charged leptons are massive\fxnote{Gloss over neutrino mass?}. Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken. Specifically, the nonzero vacuum expectation value (VEV)\fxnote{maybe just use $v$} of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$. In the process, three of the four degrees of freedom associated with the complex Higgs doublet become the longitudinal polarizations of $\Wpm$ and $\Z$, giving them mass. The remaining degree of freedom is the physical Higgs boson. Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}. These terms are interpreted as giving mass to the quarks and charged leptons, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.

@@

    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$~\cite{dine_naturalness}\fxnote{show diagrams and terms?}. Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}~\cite{cms_higgs, atlas_higgs}, a value that must be equal to the sum of the bare mass and all corrections. Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely. In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}. While it's possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work.

@@

    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly-virtual intermediate states, or (4) limited phase space in which to decay. In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the lightest particles carrying their respective conserved quantities. Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4). Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay. \fxnote{Mention neutrino, pion, kaon, some other bound state I might be forgetting?}

@@

    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways. The most straightforward SUSY LLP occurs in models with conserved R-parity, a proposed symmetry that prevents proton decay~\cite{primer}\fxnote{Be prepared to show this. Maybe add some diagrams illustrating proton decay w/o R-parity}. In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1. Conserving the product of R-parity at each vertex has two immediate phenomenological consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable. A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}.

@@

    LLPs can also arise from particular SUSY mass spectra. Models in the Split SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos. In these models, the gluino becomes long-lived when its decay to a quark and neutralino is mediated by a highly-virtual squark~\cite{kilian_split}. \fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly-degenerate LSP and NLSP. The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}.

@@

\section{The CMS Detector}\fxnote{Add pictures of everything}
    \subsection{Overview}
        \fxnote{define eta, coordinate system in general}
        \fxnote{Mention that ATLAS is similar, says Andrew}  
        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC), a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}. To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid. All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}~\cite{cms_experiment}. The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below.

@@

        The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately \num{124} million silicon pixels, each of which covers an active area of \num{100} by \SI{150}{\micro\meter^2}. The pixels are spread between four barrel layers (BPix) at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks (FPix) at $\num{29} < \mathrm{z} < \SI{52}{cm}$. The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017~\cite{cms_pixel_upgrade}.

@@

        The barrel section (EB) extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}. The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks. Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.

        The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}. Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals. \fxnote{Say what the preshower is for? Is it for pi0 rejection? If so, how and why?}

@@

        In the barrel detector (BD), four layers of DTs and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}. The maximum drift length is \SI{2}{\cm} and the single point resolution is \SI{200}{\cm}. When reconstructing a vector describing the muon momentum, the $\phi$ precision is better than \SI{100}{\micro\m} in position and \SI{1}{\milli\radian} in direction.

        Each muon endcap detector (ME) is composed of four layers of CSCs and three layers of RPCs. Each CSC has six gas gaps with radial cathode strips and nearly perpendicular planes of anode wires. The wire signal from the ionization-induced electron avalanche is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements. All in all, the CSC spacial resolution is approximately \SI{200}{\micro\m} and the angular resolution is approximately \SI{10}{\milli\radian}.

    \subsection{Trigger}
        \fxnote{Is entire detector read out at L1?}
        The trigger reduces the data writing rate from the \SI{40}{\mega\hertz} collision rate to less than \SI{1}{\kilo\hertz} so that events can be written to tape. The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT). L1 analyzes input from ECAL, HCAL, and MS with custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us. The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz\cite{cms_experiment, cms_trigger_upgrade}.

@@

        Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle. The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}. Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}. These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings~\cite{cms_stopped}.

@@

    \subsection{Disappearing Tracks}
        Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker. Specifically, models with winos as the lightest gauginos\fxnote{have these words been defined?}, such as many AMSB models\fxnote{why amsb? what is amsb?}, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate\fxnote{why? how typical?}) that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}. The nearly-degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products. The low-momentum pion is then unlikely to be reconstructed, which results in a disappearing track~\cite{atlas_disappearing}.

@@

        Pixel tracklets can be faked by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon. These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data. \fxnote{I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill}

@@

        This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps). Long-lived gluinos can appear in models such as Split SUSY, where the squarks and sleptons are quite heavy, but the gluino is relatively light. After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs. This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}. The gluino decay is suppressed by the large squark mass, which leads to its appreciable lifetime.

@@

        After estimating the background by extrapolating data from the cosmic-enriched\fxnote{enriched how? be able to explain} region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from \SI{100}{\nano\s} to \SI{1}{\micro\s}. In all cases, the expected background is less then one event. Exactly zero events are observed in every lifetime scenario. As shown in Fig.~\ref{stopped_limits}, these results are then interpreted as upper limits on the signal production cross section and mass\fxnote{mass of what?}, which are the first limits for stopped particles that decay to muons at the LHC.

@@

    \subsection{Heavy Stable Charged Particles}
        Particles that live for more than a couple \SI{}{\nano\s}\fxnote{Check this and be more exact} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying. If such a particle is also sufficiently massive, it can be categorized as a heavy stable charged particle (HSCP). HSCPs are characterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview. Probably better explained here than there}. Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}~\cite{cms_hscp}.

@@

\section{Experimental Viability of Natural SUSY}
    Interpreting current limits in the context of naturalness requires some set of criteria that determine if a model is natural. No well-defined, universally-agreed-upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}. The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's language?}.

>>>>

    Experimentally, the $\Wpm$, $\Z$, quarks, and leptons are massive. Explicit mass terms for the fermions or gauge bosons would violate the chiral and gauge symmetries of the SM Lagrangian, however, so $\SUtwoLUoneY$ must be broken\fxnote{why can't you explicitly break gauge symmetry?}. Specifically, the nonzero vacuum expectation value (VEV)\fxnote{maybe just use $v$} of the Higgs field spontaneously breaks $\SUtwoLUoneY$ to $\UoneQ$. In the process, three of the four degrees of freedom associated with the complex Higgs doublet become the longitudinal polarizations of $\Wpm$ and $\Z$, giving them mass. The remaining degree of freedom is the physical Higgs boson. Expanding the Higgs field about its VEV produces Yukawa interactions such as those in Eq.~\ref{yukawa_terms}\fxnote{This still doesn't sound right to me. The Yukawa interactions aren't produced by anything other than somebody ad-hoc adding the terms to the Lagrangian. Masses for the gauge bosons are an inherent feature of the Higgs mechanism, masses for the fermions are an ad-hoc extension, says Andrew}. These terms are interpreted as giving mass to the quarks and charged leptons, where the mass of each particle is given by the product of the Higgs VEV, $v$, and the coupling constant, $y$~\cite{sm_intro}.

@@

    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$~\cite{dine_naturalness}\fxnote{show diagrams and terms?}. Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}~\cite{cms_higgs, atlas_higgs}, a value that must be equal to the sum of the bare mass and all corrections. Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely. In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Planck scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important~\cite{giudice_naturally}. While it is possible that the bare mass and all corrections just so happen to cancel so perfectly, such miraculous fine tuning could also be a hint that a deeper physical mechanism is at work\fxnote{be prepared to offer historical examples of times when fine tuning was a hint of some deeper theory and times when it was not}.

@@

    In the SM and in BSM theories, LLPs result from any of the following conditions: (1) a symmetry that guarantees stability, (2) weak couplings to decay products, (3) highly virtual intermediate states, or (4) limited phase space in which to decay. In the SM, charge and baryon number conservation guarantee the absolute stability of the electron and proton as the lightest particles carrying their respective conserved quantities. Neutrons and muons, whose decays are shown in Fig.\ref{sm_llp_processes}, are long-lived for reasons (2), (3), and (4). Both are pure weak decays, which gives them a smaller coupling constant, but they also decay through a W-boson, which is far more massive than either parent particle, and most importantly, the proton and electron masses leave them little phase space in which to decay\fxnote{Alan doesn't think the muon-electron mass difference is that small...}.

@@

    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways. The most straightforward SUSY LLP occurs in models with conserved R-parity, a proposed symmetry that prevents proton decay~\cite{primer}\fxnote{Be prepared to show this. Maybe add some diagrams illustrating proton decay w/o R-parity}. In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1. Conserving the product of R-parity at each vertex has two immediate phenomenological consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable. A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional SUSY searches~\cite{primer}\fxnote{could mention DM as well}\fxnote{Andrew says define met and maybe explain how weakly interacting stable particles produce met}.

@@

    LLPs can also arise from particular SUSY mass spectra. Models in the Split SUSY paradigm, for example, propose that the scalar sparticles are significantly more massive than the gauginos. In these models, the gluino becomes long-lived when its decay to a quark-antiquark pair and neutralino is mediated by a highly virtual squark~\cite{kilian_split}. \fxnote{mention that Split throws out naturalness motivation?} On the other hand, some AMSB models\fxnote{explain AMSB?} predict the winos as the lightest gauginos, which leads to nearly degenerate LSP and NLSP. The NLSP wino then becomes long-lived when its decay is suppressed by the lack of available phase space~\cite{randall_sundrum_out_of_this_world}\fxnote{the winos, binos, and higgsinos are not mass eigenstates, so they are not what we search for in an experiment. We search for charginos and neutralinos, which are linear combinations of winos, binos, and higgsinos, says andrew}.

@@

\section{The CMS Detector}\fxnote{Add pictures of everything}
    \subsection{Overview}
        \fxnote{define eta, coordinate system in general}
        \fxnote{Mention that ATLAS is similar, says Andrew}  
        The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from collisions at the Large Hadron Collider (LHC)\fxnote{Make sure you are able to simply explain how the LHC works during your talk: how does it accelerate protons, how does it curve their trajectories in a circle, etc, says andrew}, a circular proton-proton collider that ran with center-of-mass energy \SI{7}{\tera\electronvolt} in 2010-11, \SI{8}{\tera\electronvolt} in 2012, and \SI{13}{\tera\electronvolt} from 2015 through to the present\fxnote{cite something}. To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{3.8}{\tesla} superconducting solenoid. All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}~\cite{cms_experiment}. The subdetectors that make up CMS are shown in Fig.~\ref{cms} and described below.

@@

        The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately \num{124} million silicon pixels, each of which covers an active area of \num{100} by \SI{150}{\micro\meter^2}. The pixels are spread between four barrel layers at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks at $\num{29} < \mathrm{z} < \SI{52}{cm}$. The upgraded pixel tracker, shown in Fig.~\ref{pixel_old_new}, should provide 4-hit tracking out to $\lvert\eta\rvert < \num{2.4}$\fxnote{define eta} and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017~\cite{cms_pixel_upgrade}.

@@

        The barrel section extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}. The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks. Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.\fxnote{Why do electrons and photons shower in the ECAL but not (usually) hadrons?, asks andrew}

        The crystals in each endcap section are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}. Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals. \fxnote{Say what the preshower is for? Is it for pi0 rejection? If so, how and why?}

@@

        In the barrel detector, four layers of DTs and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}. The maximum drift length is \SI{2}{\centi\m} and the single point resolution is \SI{200}{\micro\m}. When reconstructing a vector describing the muon momentum, the $\phi$ precision is better than \SI{100}{\micro\m} in position and \SI{1}{\milli\radian} in direction.

        Each muon endcap detector is composed of four layers of CSCs and three layers of RPCs. Each CSC has six gas gaps with radial cathode strips and nearly perpendicular planes of anode wires. The wire signal from the ionization-induced electron avalanche is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements. All in all, the CSC spacial resolution is approximately \SI{200}{\micro\m} and the angular resolution is approximately \SI{10}{\milli\radian}.

    \subsection{Trigger}
        \fxnote{Is entire detector read out at L1?}
        The trigger reduces the data writing rate from the \SI{40}{\mega\hertz} collision rate to less than \SI{1}{\kilo\hertz} so that events can be written to tape. The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT). L1 analyzes input from ECAL, HCAL, and MS with custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us. With input from all subdetectors, the HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz\cite{cms_experiment, cms_trigger_upgrade}.

@@

        Slow and stopped particle searches, on the other hand, are sensitive to detector-stable\fxnote{define?} LLPs that are far more massive\fxnote{be able to quantify} than any stable SM particle. The lower velocity of these high-mass particles can show up as increased ionization energy loss per unit distance ($\langle\frac{dE}{dx}\rangle$) or longer time-of-flight (TOF) measurements than SM particles, which generally have $\beta = \frac{v}{c} > \num{0.9}$\fxnote{check this number}~\cite{cms_hscp}. Stopped particle searches take this idea one step further and look for particles that actually come to rest inside the detector before decaying, a phenomenon that could be possible with long lifetimes and small initial kinetic energy\fxnote{how long and how small?}. These analyses look for calorimeter energy deposits or hits in the muon system that are out of time with proton bunch crossings~\cite{cms_stopped}.

@@

    \subsection{Disappearing Tracks}
        Certain models with nearly mass-degenerate LSP and NLSP have the potential to present a remarkable signal: charged particles that seem to disappear in the tracker. Specifically, models with winos as the lightest gauginos\fxnote{have these words been defined?}, such as many AMSB models\fxnote{why amsb? what is amsb?}, will have a chargino NLSP with an observable lifetime (\SI{0.2}{\nano\s} is a typical estimate\fxnote{why? how typical?}) that eventually decays to the neutralino LSP and, commonly, a pion\fxnote{why?}. The nearly degenerate masses have two important phenomenological roles: (1) increase the chargino lifetime, and (2) ensure low-momentum decay products. The low-momentum pion is then unlikely to be reconstructed, which results in a disappearing track~\cite{atlas_disappearing}.

@@

        Pixel tracklets can be faked\fxnote{don't use faked, says CMS} by random combinations of unrelated hits from nearby particles or by tracks whose pixel hits and next tracking layer hits are not properly associated, either due to a hadron suffering a hard scatter or a lepton radiating a hard photon. These backgrounds come primarily from $\ttbar$ and $\W/\Z + \mathrm{jets}$ processes, and estimates for each type of background are obtained from data. \fxnote{I initially wrote a whole big thing about how each bg was estimated, but I'm thinking it was overkill}

@@

        This analysis is interpreted in the context of two potential LLPs: gluinos and multiply charged massive particles (mchamps). Sticking with the natural SUSY theme, this discussion will focus on long-lived gluinos, which appear in models such as Split SUSY when squarks and sleptons are quite heavy, but the gluinos are relatively light. After being pair produced, gluinos form R-hadrons\fxnote{have these been defined?} and eventually decay to quark-antiquark pairs along with NLSP neutralinos, which then decay to LSP neutralinos along with muon-antimuon pairs. This process is exactly the same as in Fig.~\ref{displaced_process}, but in this case the gluino has enough time to form R-hadrons\fxnote{double check}. The gluino decay is suppressed by the large squark mass, which leads to its appreciable lifetime.

@@

        After estimating the background by extrapolating data from the cosmic-enriched\fxnote{enriched how? be able to explain} region to the signal region and determining systematic uncertainties related to the MC simulation, trigger acceptance, and luminosity, the authors calculate the expected background for LLP lifetimes ranging from $10^{-7}$ to $10^6$ s. In all cases, the expected background is less then one event. Exactly zero events are observed in every lifetime scenario. As shown in Fig.~\ref{stopped_limits}, these results are then interpreted as upper limits on the signal production cross section and mass\fxnote{mass of what?}, which are the first limits for stopped particles that decay to muons at the LHC.

@@

    \subsection{Heavy Stable Charged Particles}
        Particles that live for more than about \SI{25}{\nano\s} will appear stable in CMS and ATLAS because they can traverse the entire detector before decaying. If such a particle is also sufficiently massive, it can be categorized as a heavy stable charged particle (HSCP). HSCPs are characterized by a greater rate of energy loss via ionization due to the lower speed with which they pass through detector material\fxnote{redundant w/ overview. Probably better explained here than there}. Additionally, HSCPs can be fractionally, singly, or multiply charged, which also affects their rate of energy loss, as shown in Fig.~\ref{hscp_dedx}~\cite{cms_hscp}.

@@

\section{Experimental Viability of Natural SUSY}
    Interpreting current limits in the context of naturalness requires some set of criteria that determine if a model is natural. No well-defined, universally agreed upon criteria exist, but certain themes recur in many discussions of natural model building~\cite{craig, vestiges, evans_toward_full, feng, cornering, kim}. The following discussion lays out a simplistic set of criteria for natural SUSY models and attempts to assess the status of natural SUSY in light of current experimental limits\fxnote{Did I just steal Chris's language?}.
